%-------------------------------------------------------------------------------
%    SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project}


%-------------------------------------------------------------------------------
%    CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%-eDL---------------------------------------------------------------
  \cventry
    {Software Engineer, Data Scientist} % Role
    {eDataLyzer 개발하기} % Event
    {서울시 서초구} % Location
    {2013년 11월 - 현재, 5년 10개월,\newline 30 M/M 이상} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {eDataLyzer는 반도체의 웨이퍼 수율맵 분류와 유발요인을 상관관계 분석을 통해 찾는 제품입니다.}
        \item {이 프로젝트의 목표는 eDataLyzer를 빅데이터용으로 재개발하는 것입니다.}
        \item {그래서 저희는 이 프로젝트를 3가지 방법으로 진행했습니다.}
        \item {첫번째, 아키텍처를 모놀리틱에서 마이크로 서비스로 재구성했습니다.}
        \item {두번째, 단일팀을 역할 기반의 팀으로 재조직했습니다.(Client, Server, Algorithm, Research, Technical Sales/Support)}
        \item {세번째, C\#만 사용하는 것이 아니라 C\# + Java로 재개발했습니다.}
        \item {저는 Algorithm팀 소속으로, 주로 알고리즘을 빅데이터 신기술을 이용하여 병렬처리하는 일에 집중했습니다.}
        \item {간략하게, 3가지 방법으로 알고리즘을 병렬처리했습니다.}
        \item {첫번째, 스몰데이터용 알고리즘을 재개발했습니다.(Java, PostgreSQL, Spring)}
        \item {두번째, 하둡기반이 아닌 기술로 빅데이터용 알고리즘을 재개발했습니다.(GreenPlumDataBase PL/Java, Oracle-R)}
        \item {세번째, 하둡기반의 기술로 빅데이터용 알고리즘을 재개발했습니다.(Hadoop, BDA, Hawq, HBase, Spark, Eco system)}
        \item {이 프로젝트로 저희는 아래와 같이 많은 반도체 고객을 확보했습니다.}
        \item {한국(삼성전자, SK하이닉스, SK실트론), 일본(도시바, 샤프), 대만(TSMC), 중국(BOE)}
        \item {이 프로젝트의 유형은 PoC, pilot, production로 다양하게 확장되었습니다.}
      \end{cvitems}
    }
%-------------------------------------------------------------------

%-RL----------------------------------------------------------------
  \cventry
    {Researcher, Software Engineer} % Role
    {Research to Apply Reinforcement Learning on Semiconductor} % Event
    {Seoul, S.Korea} % Location
    {Dec. 2018 - Present, 9 months, 6 M/M} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {The goal of this project is to apply reinforcement learning on semiconductor and share the experience with team.}
        \item {I pick up 8-Puzzle as a environment for reinforcement learning.}
        \item {Here's why I pick up it in details.}
        \item {1st, in order to collaborate with teammates, I need to find the generalized environment is easy to apply Graph Theory.}
        \item {So I pick up operation management of production on semiconductor.}
        \item {2nd, in order to find suitable environment not complex one, I pick up 8-Puzzle.}
        \item {Focus on shortest path not yield, productivity, stability, automation rate, etc.}
        \item {The recent research situation is as follows.}
        \item {1st, solve 8-Puzzle by Dynamic Programming}
        \item {2nd, fail to solve 8-Puzzle by QLearning, Deep SARSA, Polish Gradient.}
        \item {The rest of the research is to find out why and how to overcome it.}
      \end{cvitems}
    }
%-------------------------------------------------------------------

%-MP----------------------------------------------------------------
  \cventry
    {Software Engineer} % Role
    {Develop Matrix Profile on Transfer System} % Event
    {Seoul, S.Korea} % Location
    {Jul. 2017 - Dec. 2017, 6 months, 2 M/M} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {The goal of this project is to predict a shutdown of motor based on time series sensed data.}
        \item {Client's product-lines(blue-collars) found out a shutdown once a year and hate this problem.}
        \item {But both client's office-lines(white-collars) and our previous algorithm didn't predict it.}
        \item {Because the algorithm focus on a vibration analysis on rotationary machine.}
        \item {So we created this project as a subproject of the previous one and led this project as below.}
        \item {1st, we found out the matrix profile which is a suitable algorithm for time series predict.}
        \item {2nd, I implemented the algorithm in python and deploy it to client. And solve the problem successfully.}
        \item {3rd, I implemented it in java and integrate with UI. Teached clients how to solve their problem through our product.}
        \item {The client of this project is Hyundai Motor. And the project type is PoC.}
      \end{cvitems}
    }
%--------------------------------------------------------------------

%-PdM----------------------------------------------------------------
  \cventry
    {Software Engineer} % Role
    {Develop Predictive Maintenance on Semiconductor} % Event
    {Seoul, S.Korea} % Location
    {Nov. 2016 - Mar. 2017, 5 months, 4 M/M} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {The goal of this project is to provide predictive maintenance on semiconductor's etching tools.}
        \item {In order to change client's empirical maintenance(condition, time), we led this project as below.}
        \item {1st, redefine input data through Self Organizing Map. And define health score as distance of each vectors of input data and observation vector.}
        \item {2nd, apply Double Exponential Weighted Moving Average to the health score. And get Remaining Useful Life for each vectors of input data.}
        \item {But we got a feedback that our product was too late for client. So we additionally led this project as follows.}
        \item {1st, detect the bottle neck of our product as the DEWMA not the SOM.}
        \item {2nd, apply Spark and HDFS on the DEWMA. And find out a tuning point.}
        \item {The client of this project is SKHynix. And the project type is pilot.}
      \end{cvitems}
    }
%--------------------------------------------------------------------

%-QA-----------------------------------------------------------------
  \cventry
    {Internship} % Role
    {QA \& Documentation on new Product} % Event
    {Seongnam, S.Korea} % Location
    {Aug. 2013 - Oct. 2013, 3 months, 5 M/M} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {During the internship, I did the following activities.}
        \item {1st, quality assurance for each feature on new product.}
        \item {2nd, modify the previous document by the user's perspective.}
      \end{cvitems}
    }
%--------------------------------------------------------------------

\end{cventries}
