%-------------------------------------------------------------------------------
%    SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}


%-------------------------------------------------------------------------------
%    CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Programming}
    {
      \begin{cvitems}
        \item {Java, SQL, Python}
        \item {In production level, I have used Java, SQL for 6 years.}
        \item {In papers or conception level, I have used Python for 2 years.}
      \end{cvitems}
    } % Skills

%---------------------------------------------------------
  \cvskill
    {Backend}
    {
      \begin{cvitems}
        \item {Spring Frameworks}
        \item {Using this, we can re-construct the previous monolithic application into micro services architect.}
        \item {Using this, we can re-build the previous configure hell party into AOP based application.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvskill
    {Database}
    {
      \begin{cvitems}
        \item {Oracle, PostgreSQL, HBase}
        \item {I used the Oracle because it's used by most semiconductor clients.}
        \item {I used the PostgreSQL because it's a alternative of the Oracle. It's easy to use and especially good for performance over price.}
        \item {I used the HBase because it's a alternative of the Oracle. It's hard to use but better than the PostgreSQL on performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvskill
    {Bigdata}
    {
      \begin{cvitems}
        \item {Java, GPDB, Hadoop, Spark}
		\item {We realized that it takes a long time to extend my previous product to big data with Java alone (Multi-Threading, Networking).}
        \item {In order to reduce the time, we find out the following Bigdata platform which enable us to focus on business logic of the product.}
        \item {1st, GPDB PL/Java is a static platform which enable us to handle data by SQL, compute data by PL/Java.}
        \item {2nd, Hadoop Spark is a dynamic platform which enable us to handle and compute data by Java. Using Hadoop with other platform not Spark, we couldn't overcome PoC.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvskill
    {ML/AI}
    {
      \begin{cvitems}
        \item {Nvidia CUDA, Keras, Tensorflow}
		\item {I used the above skills for Time Series data mining and Reinforcement Learning project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvskill
    {DevOps} % Category
    {
      \begin{cvitems}
      \item {Linux, Docker, On premise Cloud(KVM), Public Cloud Azure, AWS}
      \item {I used the above skills for support projects.}
      \end{cvitems}
    } % Skills

%---------------------------------------------------------
  \cvskill
    {Research} % Category
    {
      \begin{cvitems}
      \item {Read and implement the latest papers by python.}
      \end{cvitems}
    } % Skills

%---------------------------------------------------------
  \cvskill
    {Leadership} % Category
    {
      \begin{cvitems}
      \item {I have experience of leading two projects successfully for a year.}
      \end{cvitems}
    } % Skills

%---------------------------------------------------------
  \cvskill
    {Communications} % Category
    {
      \begin{cvitems}
      \item {I have smoothly communicated with the aggressive client, the various teammates and the academic advisor for government.}
      \end{cvitems}
    } % Skills

%---------------------------------------------------------
  \cvskill
    {Languages} % Category
    {
      \begin{cvitems}
        \item {Native in Korean}
        \item {Limited working proficiency in English.}
      \end{cvitems}
    } % Skills

\end{cvskills}
